Secondary analysis of tables

### 2019-09-19 Analysis/Analysis_Tables_New.Rmd
Publication quality figures

```{r}
max_genes <- 200 # Maximum number of genes for a network to be included
min_genes <- 10  # Minimum number of genes for a network to be included
fileNameIn0  <- "../manuscript/Tables/supplementary_table_S3.csv"   # diseases and traits, coherence new KEGG, REACTOME, CC. 2019-07-14, Kellen
# iconv -f UTF-8 -t ISO-8859-1 -c supplementary_table_S3.csv > tmp.csv
mtx0 <- read_csv(fileNameIn0) %>% as.data.frame()
rownames(mtx0) <- mtx0$Disease
```

@@

  p <- ggplot(data=mtx_traits_selected_to_plot, aes(x=Disease, y=Coherence, colour = "blue", size = Coherence)) + # label = Pvalue, 
    geom_point() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab("Normalized coherence") +
    # geom_text_repel(size = 4, colour = "black") +
    coord_flip() +
    # theme_cowplot(12) +
    theme(legend.position="none") +
    theme(axis.text = element_text(size = 12)) + 
    ggtitle(category)
}
```

@@

```{r results='hide'}
# STRING filtered plots only
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Intelligence", mtx_traits = mtx0, databases = "String Filt"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Anthropometric trait", mtx_traits = mtx0, databases = "String Filt"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular trait", mtx_traits = mtx0, databases = "String Filt"))

p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye trait", mtx_traits = mtx0, databases = "String Filt"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic trait", mtx_traits = mtx0, databases = "String Filt"))

png(filename = "../manuscript/Figures/Fig3_summary_traits.png", height = 2500, width = 5000, res = 300)
lay1 <- rbind(c(1, 2, 3))
lay2 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_anthropometric, p_cardiovascular, p_metabolic), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_eye, p_intelligence), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Intelligence", mtx_traits = mtx0, databases = "Biogrid"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Anthropometric trait", mtx_traits = mtx0, databases = "Biogrid"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular trait", mtx_traits = mtx0, databases = "Biogrid"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye trait", mtx_traits = mtx0, databases = "Biogrid"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic trait", mtx_traits = mtx0, databases = "Biogrid"))

png(filename = "../manuscript/Figures/FigS2_summary_traits_Biogrid.png", height = 2500, width = 6000, res = 300)
lay1 <- rbind(c(1, 2, 3))
lay2 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_anthropometric, p_cardiovascular, p_metabolic), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_eye, p_intelligence), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

### FigS4_summary_traits_STRING.png

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Intelligence", mtx_traits = mtx0, databases = "String"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Anthropometric trait", mtx_traits = mtx0, databases = "String"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular trait", mtx_traits = mtx0, databases = "String"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye trait", mtx_traits = mtx0, databases = "String"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic trait", mtx_traits = mtx0, databases = "String"))

png(filename = "../manuscript/Figures/FigS4_summary_traits_STRING.png", height = 2500, width = 6000, res = 300)
lay1 <- rbind(c(1, 2, 3))
lay2 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_anthropometric, p_cardiovascular, p_metabolic), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_eye, p_intelligence), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r results='hide'}
# STRING filtered plots only
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "String Filt"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "String Filt"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "String Filt"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "String Filt"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "String Filt"))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "String Filt"))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "String Filt"))

png(filename = "../manuscript/Figures/Fig4_summary_diseases.png", height = 2500, width = 5000, res = 300)
lay1 <- rbind(c(1, 2, 3, 4))
lay2 <- rbind(c(1, 2, 3, 4))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_neurologic, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "Biogrid"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "Biogrid"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "Biogrid"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "Biogrid"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "Biogrid"))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "Biogrid"))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "Biogrid"))

png(filename = "../manuscript/Figures/FigS4_summary_diseases_Biogrid.png", height = 3000, width = 8000, res = 300)
lay1 <- rbind(c(1, 2, 3, 4))
lay2 <- rbind(c(1, 2, 3, 4))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_neurologic, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "String"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "String"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "String"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "String"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "String"))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "String"))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "String"))

png(filename = "../manuscript/Figures/FigS5_summary_diseases_STRING.png", height = 3000, width = 8000, res = 300)
lay1 <- rbind(c(1, 2, 3, 4))
lay2 <- rbind(c(1, 2, 3, 4))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_neurologic, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

>>>>

```{r}
max_genes <- 200 # Maximum number of genes for a network to be included
min_genes <- 10  # Minimum number of genes for a network to be included
fileNameIn0  <- "../manuscript/Tables/supplementary_table_S3.csv"   # diseases and traits, coherence new KEGG, REACTOME, CC. 2019-07-14, Kellen
# iconv -f UTF-8 -t ISO-8859-1 -c supplementary_table_S3.csv > tmp.csv
mtx0 <- read_csv(fileNameIn0) %>% as.data.frame()
# Rename some diseases
mtx0$Disease[mtx0$Disease == "Attention deficit hyperactivity disorder"] <- "ADHD"
mtx0$Disease[mtx0$Disease == "Inflammatory bowel disease"] <- "IBD"
mtx0$Disease[mtx0$Disease == "Systemic lupus erythematosus"] <- "SLE"
mtx0$Disease[mtx0$Disease == "Age-related macular degeneration"] <- "Macular degeneration"
mtx0$Disease[mtx0$Disease == "Lupus nephritis in systemic lupus erythematosus"] <- "Lupus nephritis in SLE"

rownames(mtx0) <- mtx0$Disease
```

@@

  p <- ggplot(data=mtx_traits_selected_to_plot, aes(x=Disease, y=Coherence, colour = "blue", size = Coherence)) + # label = Pvalue, 
    geom_point() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab("Coherence") +
    # geom_text_repel(size = 4, colour = "black") +
    coord_flip() +
    # theme_cowplot(12) +
    theme(legend.position="none") +
    theme(axis.text = element_text(size = 12)) + 
    ggtitle(category)
}
```

@@

```{r results='hide'}
# STRING filtered plots only
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Intelligence", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Anthropometric trait", mtx_traits = mtx0, databases = "String Filt"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular trait", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))

p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye trait", mtx_traits = mtx0, databases = "String Filt"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic trait", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/Fig3_summary_traits.png", height = 8, width = 14, units = "in", res = 300)
lay1 <- rbind(c(1, 2, 3))
lay2 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_anthropometric, p_cardiovascular, p_metabolic), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_eye, p_intelligence), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Intelligence", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Anthropometric trait", mtx_traits = mtx0, databases = "Biogrid"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular trait", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
# p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye trait", mtx_traits = mtx0, databases = "Biogrid")) # Insufficient data
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic trait", mtx_traits = mtx0, databases = "Biogrid"))

png(filename = "../manuscript/Figures/FigS2_summary_traits_Biogrid.png", height = 6, width = 10, units = "in", res = 300)
lay1 <- rbind(c(1, 2))
lay2 <- rbind(c(1, 2))
g1 <- arrangeGrob(grobs = list(p_anthropometric, p_cardiovascular), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_metabolic, p_intelligence), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

### FigS3_summary_traits_STRING.png

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Intelligence", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Anthropometric trait", mtx_traits = mtx0, databases = "String"))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular trait", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye trait", mtx_traits = mtx0, databases = "String"))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic trait", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/FigS3_summary_traits_STRING.png", height = 8, width = 14, units = "in", res = 300)
lay1 <- rbind(c(1, 2, 3))
lay2 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_anthropometric, p_cardiovascular, p_metabolic), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_eye, p_intelligence), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r results='hide'}
# STRING filtered plots only
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "String Filt"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank())) 
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "String Filt"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "String Filt") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/Fig4_summary_diseases.png", height = 8, width = 14, units = "in", res = 300)
lay1 <- rbind(c(1, 2, 3, 4))
lay2 <- rbind(c(1, 2, 3, 4))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_neurologic, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "Biogrid"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "Biogrid"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "Biogrid") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/FigS4_summary_diseases_Biogrid.png", height = 8, width = 14, units = "in", res = 300)
lay1 <- rbind(c(1, 2, 3, 4))
lay2 <- rbind(c(1, 2, 3, 4))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric, p_neurologic, p_psychiatric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay2)
grid.arrange(g1, g2, ncol = 1)
dev.off()
```

@@

```{r }
p_intelligence <- plot(mtx_traits_selected_dotplot(category = "Autoimmune", mtx_traits = mtx0, databases = "String"))
p_anthropometric <- plot(mtx_traits_selected_dotplot(category = "Cancer", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))
p_cardiovascular <- plot(mtx_traits_selected_dotplot(category = "Cardiovascular disease", mtx_traits = mtx0, databases = "String"))
p_eye <- plot(mtx_traits_selected_dotplot(category = "Eye disease", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))
p_metabolic <- plot(mtx_traits_selected_dotplot(category = "Metabolic disease", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))
p_neurologic <- plot(mtx_traits_selected_dotplot(category = "Neurologic", mtx_traits = mtx0, databases = "String"))
p_psychiatric <- plot(mtx_traits_selected_dotplot(category = "Psychiatric", mtx_traits = mtx0, databases = "String") + theme(axis.title.y = element_blank()))

png(filename = "../manuscript/Figures/FigS5_summary_diseases_STRING.png", height = 12, width = 10, units = "in", res = 300)
lay1 <- rbind(c(1, 2))
lay2 <- rbind(c(1, 2))
lay3 <- rbind(c(1, 2, 3))
g1 <- arrangeGrob(grobs = list(p_intelligence, p_anthropometric), layout_matrix = lay1)
g2 <- arrangeGrob(grobs = list(p_neurologic, p_psychiatric), layout_matrix = lay2)
g3 <- arrangeGrob(grobs = list(p_cardiovascular, p_metabolic, p_eye), layout_matrix = lay3)

grid.arrange(g1, g2, g3, ncol = 1)
dev.off()
```
